Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2021-11-01 manuscript/manuscript.tex
Add chadwick input plot

\emergencystretch 2em  % Fix problematic long texttt
We obtained atmospherically corrected surface reflectance imaging spectroscopy data from a National Ecological Observatory (NEON) Airborne Observing Platform (AOP) scene in the Upper East River basing of Colorado, USA (39.0$^{\circ}$ N, 106.9$^{\circ}$ W) as processed by \citeA{chadwick2020integrating} and available on Google Earth Engine under the collection \texttt{users/pgbrodrick/SFA/collections/ciacorn\_priority}.
A complete description of the data and processing methods are provided in \citeA{chadwick2020integrating}.
Briefly, the scene is a mosaic from several NEON AOP flights performed in summer 2018.
NEON AOP data have a spatial resolution of XXX m and an average spectral resolution of XXX nm over the range XXX nm to XXX nm. %TODO: Fill out these values.
The atmospheric correction routine was a custom application of the Atmospheric CORrection Now (ACORN‐6LX, Imspec LLC, Glendale) software package accounting for fine-scale variation in topography and sun-sensor geometry.

\fussy  % Return to defaults
We used Google Earth Engine to manually select and extract 500 vegetation pixels from this scene (Figure~\ref{fig:sitemap}).
The pixels exhibit substantial variability in brightness and spectral character:
green reflectance (550 nm) ranges from XXX to XXX;
near-infrared reflectance (1100 nm) ranges from XXX to XXX;
and hyperspectral normalized difference vegetation index (NDVI; XXX and XXX nm bands) varies from XXX to XXX (Figure~\ref{fig:input-summary}).

@@

\begin{figure}[ht]
  \centering
  % \includegraphics[options]{figures/...}
  \caption{\label{fig:input-summary} \
    Summary of 500 input reflectance spectra selected for this study.
    Main figure shows 10 example spectra (black lines) and the full range of the input reflectance (gray shading).
    Inset figure shows a histogram of hyperspectral normalized difference vegetation index (NDVI;\@red=XXXnm, NIR=XXXnm) across the 500 input spectra.
  }
\end{figure}

>>>>

\emergencystretch 2em  % Fix problematic long texttt
We obtained atmospherically corrected surface reflectance imaging spectroscopy data from a National Ecological Observatory (NEON) Airborne Observing Platform (AOP) scene in the Upper East River basing of Colorado, USA (39.0$^{\circ}$ N, 106.9$^{\circ}$ W) as processed by \citeA{chadwick2020integrating} and available on Google Earth Engine under the collection \texttt{users/pgbrodrick/SFA/collections/ciacorn\_priority}.
Briefly, these data are from several NEON AOP flights performed in summer 2018.
NEON AOP data have a spatial resolution of 1 m and an average spectral resolution of 5 nm over the range 383 nm to 2512 nm.
The atmospheric correction routine was a custom application of the Atmospheric CORrection Now (ACORN‐6LX, Imspec LLC, Glendale) software package accounting for fine-scale variation in topography and sun-sensor geometry.

\fussy  % Return to defaults
To evaluate not just relative but also _absolute_ accuracy of plant trait retrievals, 
we used the same previously-selected canopy reflectance pixels as in \citeA{chadwick2020integrating},
which were paired with ground reference measurements of plant traits.
These pixels exhibit substantial variability in brightness and spectral character:
green reflectance (550 nm) ranges from XXX to XXX;
near-infrared reflectance (1100 nm) ranges from XXX to XXX;
and hyperspectral normalized difference vegetation index (NDVI; XXX and XXX nm bands) varies from XXX to XXX (Figure~\ref{fig:input-summary}).

A complete description of the data and processing methods are provided in \citeA{chadwick2020integrating}.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[options]{figures/input-reflectance-sample.png}
  \caption{\label{fig:input-summary} \
  Summary of input surface reflectance pixels used for this study.
  Main figure shows the darkest and brightest spectra, and every 8th spectrum sorted by brightness rank.
  Inset figure shows a histogram of hyperspectral normalized difference vegetation index (NDVI;\@red=669nm, NIR=829nm) across the 500 input spectra.
  }
\end{figure}
